% !tex jobname = cover_letter_melbourne
\documentclass[foldmarks=blmtP, fromemail, 12pt, DIV=15]{scrlttr2}
\usepackage[utf8]{inputenc}
\usepackage{libertine}
\usepackage{xspace}

\def\toaddress{%
% Selection comitee chair \\ AlbaNova University Center\\ Nordita\\ Roslagstullsbacken 23\\ SE-106 91 Stockholm\\ Sweden % Nordita
 %Selection comitee chair \\ Institut de Physique Théorique \\ CEA Saclay \\ 91191 Gif sur Yvette \\ France % Saclay
%Selection comitee chair \\ School of Mathematics and Statistics	\\ University of Melbourne
%Parkville VIC 3010	\\ Australia % Melbourne	
%Prof. Dr. Beisert, Niklas
Post-doctoral selection committee
\\
%Wolfgang-Pauli-Str. 27
%Institut de Physique Théorique, CEA Saclay \\ 91191 Gif sur Yvette, France % Saclay
C.N. Yang Institute for Theoretical Physics
\\
Stony Brook University
\\
Stony Brook, N.Y. 11794-3840, U.S.A.
%\\
%8093 Zürich, Switzerland
}
\newcommand{\positionname}{%
% FELLOW20% Nordita
% POSTDOCMATHPHYS [\#15155]% Saclay
%UniMelb-RFMP [\#15201, 0049490] % Melbourne	
%\#17642\xspace
POSTDOC21 [\#17393]
}
\newcommand{\atinstitute}{%
% at Nordita%
% at IPhT%
%in the school of Mathematics and Statistics 
%at IPhT Saclay\xspace
C.N. Yang Institute of Theoretical Physics\xspace
}
\def\addressto{%
%selection comitee members% Norditam
members of the selection committee\xspace
%Prof. Beisert\xspace
}
\def\ingroup{%
in the mathematical physics group\xspace% Nordita
}
\newcommand{\aspostedin}{%
as posted in \href{https://www.mathjobs.org/jobs/UniMelb/RFMP}{mathjobs.org}%
}
\newcommand{\PIlist}{%
% Hubert Saleur and Jesper Jacobsen% Saclay
% 
}


\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[british]{babel}

\usepackage{xifthen}
\usepackage{xspace}

\usepackage{paralist}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{txfonts}

\usepackage[colorlinks]{hyperref}
\usepackage{cleveref}

% \setkomafont{author}{\normalfont}
% \setkomafont{date}{\normalfont}
% \setkomafont{title}{\scshape\small}

\begin{document}
\setkomavar{fromname}{Giridhar V. \MakeUppercase{Kulkarni}}
\setkomavar{fromaddress}{14 bis, Rue de Montigny \\ 21000 Dijon, France}
\setkomavar{fromemail}{giridhar.kulkarni@protonmail.ch}
\setkomavar{subject}{Application for a post-doctoral position (\positionname)}
\setkomavar{signature}{Giridhar V. Kulkarni}
\begin{letter}{%
\toaddress
}
\opening{Dear \addressto,}
%I am researcher in mathematical physics recently graduated with a PhD degree from the University of Burgundy.
%I did my PhD thesis in supervision of Prof. Nikolai Kitanine on the `Asymptotic analysis of the form-factors of quantum spin chains'.
%I sucessfully defended my thesis on 20th November 2020.
%\par
I am writing to apply for the postoctoral position \positionname \ingroup\space\atinstitute. 
Previously, I was a PhD student workind under the direction of Nikolai Kitanine at University of Burgundy, I defended my thesis "Asymptotic analysis of the form-factors of quantum spin chains" on 20th Novermber this year.

I am interested in studying the hidden symmetries of exactly solvable models / quantum integrable systems and their applications in development of non-perturbative approaches for exact computations of correlation functions.
In my doctoral research work, I worked with my advisor on algebraic Bethe ansatz method for form-factors of quantum spin chains, in which we developed a new technique to compute form-factors in thermodynamic limit.
It was used to reproduce the previous result from the q-vertex operator algebra approach for the 2-spinon form-factors of XXX model and we've also found some novel results for the higher form-factors containing bound state using this approach.
\par
I would like to continue to work on similar problems, that are related with quantum integrability and/or conformal symmetries of field theories. That is the particular reason that I am applying for this post-doctroal fellowship.
If am selected, I will be delighted to work with Prof. V. Korepin and I hope that I will also have numerous opportunities to discussions with emeritus fellows in the institute: B. McCoy, L. Takhtadzhyan, that will be greatly helpful in development of my academic career. 
\ps{Thank you all for your consideration!}
\closing{Yours truly,}
\vspace{-1em}
\setkomavar*{enclseparator}{Sumbissions}
\encl{CV, Research Statement, List of publications}
\end{letter}
\end{document}
