% !tex jobname = cover_letter_melbourne
\documentclass[foldmarks=blmtP, fromemail, 12pt, DIV=15]{scrlttr2}
\usepackage[utf8]{inputenc}
\usepackage{libertine}
\usepackage{xspace}

\newcommand{\toaddress}{%
% Selection comitee chair \\ AlbaNova University Center\\ Nordita\\ Roslagstullsbacken 23\\ SE-106 91 Stockholm\\ Sweden % Nordita
 %Selection comitee chair \\ Institut de Physique Théorique \\ CEA Saclay \\ 91191 Gif sur Yvette \\ France % Saclay
%Selection comitee chair \\ School of Mathematics and Statistics	\\ University of Melbourne
%Parkville VIC 3010	\\ Australia % Melbourne	
Prof. Dr. Beisert, Niklas
\\
Wolfgang-Pauli-Str. 27
\\
8093 Zürich, Switzerland
}
\newcommand{\positionname}{ %
% FELLOW20% Nordita
% POSTDOCMATHPHYS [\#15155]% Saclay
UniMelb-RFMP [\#15201, 0049490] % Melbourne	
}
\newcommand{\atinstitute}{ %
% at Nordita%
% at IPhT%
%in the school of Mathematics and Statistics 
in your research group at ITP-ETH Zurich
}
\newcommand{\addressto}{ %
%selection comitee members% Nordita
Prof. Beisert\xspace
}
\newcommand{\ingroup}{ %
in mathematical physics group% Nordita
}
\newcommand{\aspostedin}{ %
as posted in \href{https://www.mathjobs.org/jobs/UniMelb/RFMP}{mathjobs.org}%
}
\newcommand{\PIlist}{ %
% Hubert Saleur and Jesper Jacobsen% Saclay
% 
}


\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[british]{babel}

\usepackage{xifthen}
\usepackage{xspace}

\usepackage{paralist}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{txfonts}

\usepackage[colorlinks]{hyperref}
\usepackage{cleveref}

% \setkomafont{author}{\normalfont}
% \setkomafont{date}{\normalfont}
% \setkomafont{title}{\scshape\small}

\begin{document}
\setkomavar{fromname}{Giridhar V. \textsc{Kulkarni}}
\setkomavar{fromaddress}{14 bis, Rue de Montigny \\ 21000 Dijon, France}
\setkomavar{fromemail}{giridhar.kulkarni@protonmail.ch}
\setkomavar{subject}{Application for a post-doctoral position\atinstitute}
\setkomavar{signature}{Giridhar V. Kulkarni}
\begin{letter}{%
\toaddress
}
\opening{Dear {\addressto},}

I am researcher in mathematical physics recently graduated with a PhD degree from the University of Burgundy.
I did my PhD thesis in supervision of Prof. Nikolai Kitanine on the `Asymptotic analysis of the form-factors of quantum spin chains'.
I sucessfully defended my thesis on 20th November 2020.
\par
I am writing to apply for the postoctoral position in your group, after I saw the call for applications on INSPIRE. 
I've submitted my CV, list of publications and a copy of my PhD thesis to the dedicated portal along with this letter. 
\par
Previously I've worked on algebraic Bethe ansatz techniques for the computations of form-factors and correlations of quantum spin chains. Jointly with my thesis advisor, we developed a new ABA based technique for taking thermodynamic limit of form-factor which led to us some very interesting results.
\\
I would like to continue to work on problems related with quantum integrable systems, which is why I am applying to the post-doctroal position in your group.
You have worked on the relationship of integrable quantum spin chains to the AdS-CFT correspondance.
I find it fascinating topic, especially because of its implications and potential applications that goes both ways. I am eager to learn more about the integrability in AdS-CFT and work on its developments.
Although I have not previously worked on problems directly related to AdS/CFT, I believe that my background with previous work on quantum spin chains will be extremely useful in these endeavours.
\ps{Please accept my sincere apologies for the delayed application, I thank you for considering my application.}
% \\ 
\closing{Yours truly,}
\setkomavar*{enclseparator}{Attachements}
\encl{%
\vspace{-1em}
\begin{enumerate}
	\item CV, List of publications, teachings and talks.
	\vspace{-1em}
	\item Research statement
	\vspace{-1em}
	\item Final version of PhD Thesis
\end{enumerate}
}
\end{letter}
\end{document}
